\clearpage
\phantomsection
\chapter*{ACKNOWLEDGEMENT}
\addcontentsline{toc}{chapter}{ACKNOWLEDGEMENT}

First of all, I would like to express my deepest gratitude to my advisor, \textbf{Dr. HAS Sothea}, for his valuable guidance, continuous support, and encouragement throughout the completion of this thesis. His advice, knowledge, and thoughtful feedback have helped me improve my work and stay motivated during this research journey.

I would also like to sincerely thank my supervisor, \textbf{Dr. PHAUK Sokkhey}, for his dedicated mentorship, helpful suggestions, and constant support. I am truly grateful for the opportunity to learn and work in a supportive and collaborative environment at \textbf{ReDa Lab}, which has contributed greatly to my academic growth.

My sincere appreciation also goes to \textbf{Dr. LIN Mongkolsery}, Head of the Department of Applied Mathematics and Statistics, \textbf{Dr. PHAUK Sokkhey}, Deputy Head of the Department, and all lecturers in the AMS Department. Their dedication to teaching and supporting students has created a positive and encouraging academic environment.

I would also like to thank the leadership and staff of the Institute of Technology of Cambodia. In particular, I am grateful to \textbf{H.E. Dr. PO Kimtho}, Director of the Institute, for his leadership and commitment to promoting academic excellence. The learning environment at ITC has played an important role in both my academic and personal development.

Finally, I would like to express my heartfelt thanks to my family and friends for their love, patience, and encouragement. My family has always supported me emotionally and practically whenever I needed help. My friends also gave me motivation, advice, and companionship, which made this journey more meaningful and manageable. This thesis would not have been possible without the support of all these people.

